---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "graphics/README-",
  cache=FALSE,
  fig.align='center'
)
set.seed(1)
```

## Prettified Base Graphics

Anyone who uses R Base graphics, have a 100 and 1 tweaks that they use to make the 
figures more presentable. This package aims to capture the tweaks in one place. By _masking_
standard plotting functions, we can automatically make base graphics a bit more pretty.

## Installation

The package is still being developed and the API is subject to change. To install the package from
github, use **devtools**

```{r, eval=FALSE}
devtools::install_github("jumpingrivers/prettyB")
```
The package can then be loaded in the usual way

```{r, message=FALSE}
## Warning: base function masking
library("prettyB")
```

## Usage

All plotting functions work exactly as before, with the same inputs. The difference 
is that the defaults have been changed. For example, compare

```{r, fig.width=12}
op = par(mfrow = c(1, 2))
graphics::plot.default(iris$Sepal.Length, iris$Sepal.Width)
plot(iris$Sepal.Length, iris$Sepal.Width)
```

The second `plot()` function call is from the **prettyB** package.  

There are currently two themes: `expand` (default) and `minimal`:

```{r, fig.width=12, echo=c(-1, -5)}
par(mfrow = c(1, 2))
theme_set("minimal")
graphics::plot.default(iris$Sepal.Length, iris$Sepal.Width, 
     main="Classic Iris Dataset", xlab="Length", ylab="Width")
plot(iris$Sepal.Length, iris$Sepal.Width, 
     main="Classic Iris Dataset", xlab="Length", ylab="Width")
par(op)
```

## Other plots

The package also prettifies other functions (examples below use the `minimal` theme).

  * barplots
    ```{r, echo=-1}
    par(mfrow = c(1, 2), cex=0.9)
    graphics::barplot.default(VADeaths, main = "Death Rates in Virginia")
    barplot(VADeaths, main = "Death Rates in Virginia")
    ```
  * qqplots
    ```{r, echo=-1}
    par(mfrow = c(1, 2))
    x = rnorm(20)
    stats:::qqnorm.default(x)
    qqnorm(x)
    ```
  * Histograms
    ```{r, echo=-1}
    par(mfrow=c(1, 2))
    z = rt(100, 2)
    graphics::hist.default(z, main="The t-distribution")
    hist(z, main="The t-distribution")
    ```


## TODO

  * Think a bit more about palettes
  * Vignettes: What defaults have been changed.
  * Boxplots
  * Package building: Can I ignore the warnings?
  * Tests
