---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = FALSE,
  fig.align = 'center'
)
set.seed(1)
```

## Prettified Base Graphics

[![R-CMD-check](https://github.com/jumpingrivers/prettyB/workflows/R-CMD-check/badge.svg)](https://github.com/jumpingrivers/prettyB/actions)
[![CRAN](http://www.r-pkg.org/badges/version/prettyB)](https://cran.r-project.org/package=prettyB)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Coverage status](https://codecov.io/gh/jumpingrivers/prettyB/branch/master/graph/badge.svg)](https://codecov.io/github/jumpingrivers/prettyB?branch=master)
[![Downloads](http://cranlogs.r-pkg.org/badges/prettyB?color=brightgreen)](https://cran.r-project.org/package=prettyB)

Anyone who uses R Base graphics, have a 100 and 1 tweaks that they use to make the 
figures more presentable. This package aims to capture the tweaks in one place. 

## Installation

The package is still being developed and the graphs are subject to change.
The package is on CRAN and can be installed in the usual way
```{r eval = FALSE}
install.packages("prettyB")
```
To install the dev version, try

```{r, eval=FALSE}
devtools::install_github("jumpingrivers/prettyB")
```
The package can then be loaded in the usual way

```{r, message=FALSE}
library("prettyB")
```

## Usage

All plotting functions work exactly as before, with the same inputs. The difference 
is that the defaults have been changed. For example, compare

```{r, plot-minimal,fig.width=12}
op = par(mfrow = c(1, 2))
plot(iris$Sepal.Length, iris$Sepal.Width)
plot_p(iris$Sepal.Length, iris$Sepal.Width)
```

When you first call a __prettyB__, it changes the underlying `par()` and
`palette()`. You can reset this via

```{r}
prettyB::reset_prettyB()
```

The core idea of __prettyB__ is that no new arguments are introducted to the
plot functions. This means, that no changes to existing code
are required

```{r, plot-minimal-full,fig.width=6, echo = -1}
op = par(mfrow = c(1, 1))
plot_p(iris$Sepal.Length, iris$Sepal.Width, 
     xlab = "Length", ylab = "Width",
     main = "The Iris data set", 
     sub = "I hate this data too")
```

## Other plots

The package also prettifies other functions

  * Histograms
    ```{r, echo=c(-1, -2)}
    prettyB::reset_prettyB()
    par(mfrow = c(1, 2))
    z = rt(100, 4)
    hist(z, main = "The t-distribution")
    hist_p(z, main = "The t-distribution")
    ```
  * barplots
    ```{r, echo=-1}
    par(mfrow = c(1, 2), cex = 0.9)
    barplot(VADeaths, main = "Death Rates in Virginia")
    barplot_p(VADeaths, main = "Death Rates in Virginia")
    ```

## Package Rationale

This package is __not__ a replacement for __ggplot2__ or other R related plotting packages. Instead, it has a few simple aims

 * provide package authors a low dependency method of making their plots look pretty
 * provide academics with a way of generating nice plots, but not worry about future changes in R
 * provide a simple way for improving the look and feel of plots in teaching

Since the generated plots by __prettyB__ use standard base graphics, with no new arguments, this makes plots future proof. As a fall-back, just remove the `_p`.

I picked up the general style a few years ago, but the book
[Fundamentals of Data Visualization](https://www.amazon.com/Fundamentals-Data-Visualization-Informative-Compelling/dp/1492031089/) has made it a bit 
more consist. The author also provided a free 
[online](https://serialmentor.com/dataviz/) version.

## Other information

 * If you have any suggestions or find bugs, please use the github [issue tracker](https://github.com/jumpingrivers/prettyB/issues)
 * Feel free to submit pull requests

---

Development of this package was supported by [Jumping Rivers](https://www.jumpingrivers.com)
