---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = FALSE,
  fig.align = 'center'
)
set.seed(1)
```

## Prettified Base Graphics

[![Build Status](https://travis-ci.org/jumpingrivers/prettyB.svg?branch=master)](https://travis-ci.org/jumpingrivers/prettyB)
[![Coverage status](https://codecov.io/gh/jumpingrivers/prettyB/branch/master/graph/badge.svg)](https://codecov.io/github/jumpingrivers/prettyB?branch=master)

Anyone who uses R Base graphics, have a 100 and 1 tweaks that they use to make the 
figures more presentable. This package aims to capture the tweaks in one place. By _masking_
standard plotting functions, we can automatically make base graphics a bit more pretty.

## Installation

The package is still being developed and the API is subject to change. To install the package from
github, use **devtools**

```{r, eval=FALSE}
devtools::install_github("jumpingrivers/prettyB")
```
The package can then be loaded in the usual way

```{r, message=FALSE}
library("prettyB")
```

## Usage

All plotting functions work exactly as before, with the same inputs. The difference 
is that the defaults have been changed. For example, compare

```{r, plot-minimal,fig.width=12}
op = par(mfrow = c(1, 2))
graphics::plot.default(iris$Sepal.Length, iris$Sepal.Width)
plot(iris$Sepal.Length, iris$Sepal.Width)
```

The second `plot()` function call is from the **prettyB** package.  

There are currently two themes: `expand` and `minimal`(default):

```{r, plot-expand, fig.width=12, echo=-5}
theme_set("expand")
par(mfrow = c(1, 2))
graphics::plot.default(iris$Sepal.Length, iris$Sepal.Width, 
     main="Classic Iris Dataset", xlab="Length", ylab="Width")
plot(iris$Sepal.Length, iris$Sepal.Width, 
     main="Classic Iris Dataset", xlab="Length", ylab="Width")
par(op)
```

<!-- ## Other plots -->

<!-- The package also prettifies other functions, currently only qqplots. -->

<!--   * qqplots -->
<!--     ```{r, qqplots,echo=-1} -->
<!--     theme_set("minimal") -->
<!--     par(mfrow = c(1, 2)) -->
<!--     x = rnorm(20) -->
<!--     stats:::qqnorm.default(x) -->
<!--     qqnorm(x) -->
<!--     ``` -->
  <!-- * Histograms -->
  <!--   ```{r, echo=-1} -->
  <!--   par(mfrow=c(1, 2)) -->
  <!--   z = rt(100, 2) -->
  <!--   graphics::hist.default(z, main="The t-distribution") -->
  <!--   hist(z, main="The t-distribution") -->
  <!--   ``` -->
  <!-- * barplots -->
  <!--   ```{r, echo=-1} -->
  <!--   par(mfrow = c(1, 2), cex=0.9) -->
  <!--   graphics::barplot.default(VADeaths, main = "Death Rates in Virginia") -->
  <!--   barplot(VADeaths, main = "Death Rates in Virginia") -->
  <!--   ``` -->

## Package Rationale

This package is __not__ a replacement for __ggplot2__ or other R related plotting packages. Instead, it has a few simple aims

 * provide package authors a low dependency method of making their plots look pretty
 * provide academics with a way of generating nice plots, but not worry about future changes in R
 * provide a simple way for improving the look and feel of plots in teaching
 
Since the generated plots by __prettyB__ use standard base graphics, with no new arguments, this makes plots future proof. As a fall-back, just don't load the package. 

## Other information

 * If you have any suggestions or find bugs, please use the github [issue tracker](https://github.com/jumpingrivers/prettyB/issues)
 * Feel free to submit pull requests

### TODO

  * Box plots, barplots, histograms
  * Think a bit more about palettes
  * Vignettes: What defaults have been changed.

---

Development of this package was supported by [Jumping Rivers](https://www.jumpingrivers.com)


