---
title: "Introduction to prettyB"
author: "Colin Gillespie"
vignette: >
  %\VignetteIndexEntry{Introduction to prettyB}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---
```{r include = FALSE}
knitr::opts_chunk$set(results = "hide", echo = TRUE )
set.seed(1)
library(prettyB)
```

## Introduction

The __prettyB__ changes the default values of some standard plotting functions.
It is __not__ a replacement for __ggplot2__ (or other plotting packages),
instead, it's meant to just make the base graphics a little bit nicer.
Due to the underlying structure of base graphics & S3 objects, some things aren't possible. 
In particular, changing how non-exported plot-methods are displayed.

The general idea is by simply loading the __prettyB__ package, plots
just become a bit nicer! The current methods that are available are

 * `plot()`
 * `barplot()`
 * `boxplot()`
 * `hist()`

## Histogram examples

The important point to note with this histogram method is the `breaks` 
argument now has a new default. Instead of `breaks = "Sturges"`, the
default is `breaks = "fd"`. In general, this is a better default (but
not always)
```{r, echo = c(-1, -2)}
op = par(mfrow = c(1, 2))
reset_prettyB()
x = rlnorm(100)
graphics::hist.default(x)
hist(x)
```

Standard arguments work as well
```{r, echo = c(-1, -2)}
op = par(mfrow = c(1, 2))
reset_prettyB()
y = rnorm(100)
graphics::hist.default(y, main = "Base Graphics", sub = "Sub heading", 
                       xlab = "x-axis", ylab = "y-axis")
hist(y, main = "prettyB",  sub = "Sub heading", xlab = "x-axis", ylab = "y-axis")
```

Colours and frequencies also work as is expected
```{r, echo = c(-1, -2)}
op = par(mfrow = c(1, 2))
reset_prettyB()
z = rt(100, 4)
graphics::hist.default(z, col = "grey60", freq = FALSE)
hist(z, col = "grey60", freq = FALSE)
```

## Barplot examples

The `barplot()` has an amazing number of different configurations.

```{r, out.width="100%"}
op = par(mfrow = c(1, 2))
reset_prettyB()
require(grDevices) # for colours
tN <- table(Ni <- stats::rpois(100, lambda = 3))
graphics::barplot.default(tN)
barplot(tN)
```
The following examples are taken directly from the example page of `?barplot`.
This means that sometimes the colours clash.
```{r}
reset_prettyB()
r = graphics::barplot.default(tN, col = rainbow(20))
#- type = "h" plotting *is* 'bar'plot
lines(r, tN, type = "h", col = "red", lwd = 2)
r = barplot(tN, col = rainbow(20))
#- type = "h" plotting *is* 'bar'plot
lines(r, tN, type = "h", col = "red", lwd = 2)
```
Spacing and titles still work
```{r}
reset_prettyB()
graphics::barplot.default(tN, space = 1.5, axisnames = FALSE,
        sub = "barplot(..., space= 1.5, axisnames = FALSE)")
barplot(tN, space = 1.5, axisnames = FALSE,
        sub = "barplot(..., space= 1.5, axisnames = FALSE)")
```
So does the `beside` argument.
```{r}
reset_prettyB()
graphics::barplot.default(VADeaths, beside = TRUE,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),
        legend = rownames(VADeaths), ylim = c(0, 100))

barplot(VADeaths, beside = TRUE,
        col = c("lightblue", "mistyrose", "lightcyan",
                "lavender", "cornsilk"),
        legend = rownames(VADeaths), ylim = c(0, 100))
```

## Other plotting methods

```{r}
par(mfrow = c(1, 2))
plot(1:100, rnorm(100), xlab = "X", ylab = "Y")
boxplot(rnorm(100))
```














